---
title: "First_RQ"
author: "Song Zhang"
date: '2022-06-07'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
mb <- read.csv("new_mb.csv", as.is = TRUE)
mb_2digind <- read.csv("new_mb_2dig_ind.csv", as.is = TRUE)
mb_3digind <- read.csv("new_mb_3dig_ind.csv", as.is = TRUE)
```

```{r}
names(mb_3digind)
```

```{r}
mb_lmdata <- mb[, -c(1, 2, 3, 5, 6)]
mb_2digindlmdata <- mb_2digind[, -c(1, 2, 3, 5, 6)]
mb_3digindlmdata <- mb_3digind[, -c(1, 2, 3, 5, 6)]
mb_lmdata$Location.indicator...code <- mb_lmdata$Location.indicator...code -1
mb_2digindlmdata$Location.indicator...code <- mb_2digindlmdata$Location.indicator...code -1
mb_3digindlmdata$Location.indicator...code <- mb_3digindlmdata$Location.indicator...code -1
names(mb_3digindlmdata)
head(mb_lmdata)
```

```{r}
#install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
my_data <- mb_3digindlmdata[, -c(1, 3, 7, 8, 9)]
chart.Correlation(my_data, histogram=TRUE, pch=10)
```

## Backwards selection

```{r}
names(my_data)
```

```{r}
lm0 <- lm(Net.Profit.Loss ~ ., data=my_data) 
summary(lm0)
```

```{r}
mydata1 <- my_data[, -c(1)]
lm1 <- lm(Net.Profit.Loss ~ ., data=mydata1) 
summary(lm1)
```

```{r}
mydata2 <- mydata1[, -c(9)]
lm2 <- lm(Net.Profit.Loss ~ ., data=mydata2) 
summary(lm2)
```

```{r}
mydata3 <- mydata2[, -c(7)]
lm3 <- lm(Net.Profit.Loss ~ ., data=mydata3) 
summary(lm3)
```

```{r}
mydata4 <- mydata3[, -c(10)]
lm4 <- lm(Net.Profit.Loss ~ ., data=mydata4) 
summary(lm4)
```

```{r}
mydata5 <- mydata4[, -c(11)]
lm5 <- lm(Net.Profit.Loss ~ ., data=mydata5) 
summary(lm5)
```

```{r}
mydata6 <- mydata5[, -c(8)]
lm6 <- lm(Net.Profit.Loss ~ ., data=mydata6) 
summary(lm6)
```

```{r}
names(mydata6)
```



```{r}
mydata7 <- mydata6[, -c(5)]
lm7 <- lm(Net.Profit.Loss ~ ., data=mydata7) 
summary(lm7)
```

### For Rural

```{r}
mb_3ind_rural<-mydata7[ which(mb_3digind$Location.indicator=='Rural'), ]
```

```{r}
names(mb_3ind_rural)
```


```{r}
lm_rural <- lm(Net.Profit.Loss ~ ., data=mb_3ind_rural) 
summary(lm_rural)
```

#### Correlation Matrix rural medium

```{r}
#install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
my_data_rural <- my_data[ which(mb_3digind$Location.indicator=='Rural'), ]
chart.Correlation(my_data_rural, histogram=TRUE, pch=10)
```


#### backwards selection for rural

```{r}
lm0_rural <- lm(Net.Profit.Loss ~ ., data=my_data_rural) 
summary(lm0_rural)
```





```{r}
my_data_rural1 <- my_data_rural[, -c(10)]
lm1_rural <- lm(Net.Profit.Loss ~ ., data=my_data_rural1) 
summary(lm1_rural)
```

```{r}
my_data_rural2 <- my_data_rural1[, -c(10)]
lm2_rural <- lm(Net.Profit.Loss ~ ., data=my_data_rural2) 
summary(lm2_rural)
```



```{r}
my_data_rural3 <- my_data_rural2[, -c(2)]
lm3_rural <- lm(Net.Profit.Loss ~ ., data=my_data_rural3) 
summary(lm3_rural)
```

```{r}
my_data_rural4 <- my_data_rural3[, -c(12)]
lm4_rural <- lm(Net.Profit.Loss ~ ., data=my_data_rural4) 
summary(lm4_rural)
```



```{r}
my_data_rural5 <- my_data_rural4[, -c(1)]
lm5_rural <- lm(Net.Profit.Loss ~ ., data=my_data_rural5) 
summary(lm5_rural)
```


```{r}
my_data_rural6 <- my_data_rural5[, -c(8)]
lm6_rural <- lm(Net.Profit.Loss ~ ., data=my_data_rural6) 
summary(lm6_rural)
```

```{r}
my_data_rural7 <- my_data_rural6[, -c(8)]
lm7_rural <- lm(Net.Profit.Loss ~ ., data=my_data_rural7) 
summary(lm7_rural)
```



```{r}
my_data_rural8 <- my_data_rural7[, -c(5)]
lm8_rural <- lm(Net.Profit.Loss ~ ., data=my_data_rural8) 
summary(lm8_rural)
```

```{r}
my_data_rural9 <- my_data_rural8[, -c(7)]
lm9_rural <- lm(Net.Profit.Loss ~ ., data=my_data_rural9) 
summary(lm9_rural)
```







### For urban

```{r}
mb_3ind_urban<-mydata7[ which(mb_3digind$Location.indicator=='Urban'), ]
lm7_urban <- lm(Net.Profit.Loss ~ ., data=mb_3ind_urban) 
summary(lm7_urban)
```

#### Correlation Matrix urban medium

```{r}
#install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
my_data_urban <- my_data[ which(mb_3digind$Location.indicator=='Urban'), ]
chart.Correlation(my_data_urban, histogram=TRUE, pch=10)
```




############# end of backwards selection ###########


```{r}
library(ggplot2)
my_data <- mb_lmdata
ggplot(my_data, aes(x = Total.expenses, y = Net.Profit.Loss, colour=as.factor(Location.indicator...code))) + geom_point() + geom_smooth(method = lm) 
```

```{r}
library(ggplot2)
my_data <- mb_2digindlmdata
ggplot(my_data, aes(x = Total.expenses, y = Net.Profit.Loss, colour=as.factor(Location.indicator...code))) + geom_point() + geom_smooth(method = lm) 
```

```{r}
library(ggplot2)
my_data <- mb_3digindlmdata
Location = as.factor(my_data$Location.indicator...code)
ggplot(my_data, aes(x = Total.expenses, y = Net.Profit.Loss, colour=Location)) + geom_point() + geom_smooth(method = lm) 
```

```{r}
my_data <- mb_lmdata
mb_lm <- lm(Net.Profit.Loss ~Total.expenses*Location.indicator...code, data=my_data) 
summary(mb_lm)
```

```{r}
library(ggplot2)
my_data <- mb_lmdata
ggplot(my_data, aes(x = Total.expenses, y = Net.Profit.Loss, colour=as.factor(Location.indicator...code))) + geom_point() + geom_abline(slope = -0.56469, intercept = 5493.68579, colour = 'red') + geom_abline(slope = -0.76408, intercept = 7419.077, colour = 'dark blue')
#+
#scale_x_continuous(limits = c(0,300)) +
#scale_y_continuous(limits = c(0,300))
#plot(my_data$Net.Profit.Loss~my_data$Total.expenses)
#abline(mb_lm, col="blue", lwd=3)
#+ geom_smooth(method = lm) 
```

```{r}
my_data <- mb_2digindlmdata
mb_lm <- lm(Net.Profit.Loss ~Total.expenses*Location.indicator...code, data=my_data) 
summary(mb_lm)
```

```{r}
library(ggplot2)
my_data <- mb_2digindlmdata
ggplot(my_data, aes(x = Total.expenses, y = Net.Profit.Loss, colour=as.factor(Location.indicator...code))) + geom_point() + geom_abline(slope = -0.92051, intercept = 8336.38891, colour = 'red') + geom_abline(slope = -0.82835, intercept = 7854.27, colour = 'dark blue')
#+
#scale_x_continuous(limits = c(0,300)) +
#scale_y_continuous(limits = c(0,300))
#plot(my_data$Net.Profit.Loss~my_data$Total.expenses)
#abline(mb_lm, col="blue", lwd=3)
#+ geom_smooth(method = lm) 
```

```{r}
my_data <- mb_3digindlmdata
mb_lm <- lm(Net.Profit.Loss ~Total.expenses*Location.indicator...code, data=my_data) 
summary(mb_lm)
```

```{r}
library(ggplot2)
my_data <- mb_3digindlmdata
ggplot(my_data, aes(x = Total.expenses, y = Net.Profit.Loss, colour=as.factor(Location.indicator...code))) + geom_point() + geom_abline(slope = -0.4679, intercept = 4651.4470, colour = 'red') + geom_abline(slope = -0.7594, intercept = 7400.342, colour = 'dark blue')
#+
#scale_x_continuous(limits = c(0,300)) +
#scale_y_continuous(limits = c(0,300))
#plot(my_data$Net.Profit.Loss~my_data$Total.expenses)
#abline(mb_lm, col="blue", lwd=3)
#+ geom_smooth(method = lm) 
```

                 colour = 'red'---rural  | colour = 'dark blue'---urban

slope = -0.56469, intercept = 5493.68579 \| slope = -0.76408, intercept = 7419.077 \| All slope = -0.92051, intercept = 8336.38891 \| slope = -0.82835, intercept = 7854.27 \| 2dig slope = -0.4679, intercept = 4651.4470 \| slope = -0.7594, intercept = 7400.342 \| 3dig




```{r}
my_data <- mb_lmdata
mb_lm_paral <- lm(Net.Profit.Loss~Total.expenses+Location.indicator...code, data=my_data) 
summary(mb_lm_paral)
```

```{r}
library(ggplot2)
my_data <- mb_lmdata
ggplot(my_data, aes(x = Total.expenses, y = Net.Profit.Loss, colour=as.factor(Location.indicator...code))) + geom_point() + geom_abline(slope = -0.69866, intercept = 6632.99072, colour = 'red') + geom_abline(slope = -0.69866, intercept = 6824.647, colour = 'dark blue')
#+
#scale_x_continuous(limits = c(0,300)) +
#scale_y_continuous(limits = c(0,300))
#plot(my_data$Net.Profit.Loss~my_data$Total.expenses)
#abline(mb_lm, col="blue", lwd=3)
#+ geom_smooth(method = lm) 
```

```{r}
my_data <- mb_2digindlmdata
mb_lm_paral <- lm(Net.Profit.Loss~Total.expenses+Location.indicator...code, data=my_data) 
summary(mb_lm_paral)
```

```{r}
library(ggplot2)
my_data <- mb_2digindlmdata
ggplot(my_data, aes(x = Total.expenses, y = Net.Profit.Loss, colour=as.factor(Location.indicator...code))) + geom_point() + geom_abline(slope = -0.86964, intercept = 7933.03356, colour = 'red') + geom_abline(slope = -0.86964, intercept = 8210.962, colour = 'dark blue')
#+
#scale_x_continuous(limits = c(0,300)) +
#scale_y_continuous(limits = c(0,300))
#plot(my_data$Net.Profit.Loss~my_data$Total.expenses)
#abline(mb_lm, col="blue", lwd=3)
#+ geom_smooth(method = lm) 
```

```{r}
my_data <- mb_3digindlmdata
mb_lm_paral <- lm(Net.Profit.Loss~Total.expenses+Location.indicator...code, data=my_data) 
summary(mb_lm_paral)
```

```{r}
library(ggplot2)
my_data <- mb_3digindlmdata
ggplot(my_data, aes(x = Total.expenses, y = Net.Profit.Loss, colour=as.factor(Location.indicator...code))) + geom_point() + geom_abline(slope = -0.67259, intercept = 6423.53835, colour = 'red') + geom_abline(slope = -0.67259, intercept = 6603.554, colour = 'dark blue')
#+
#scale_x_continuous(limits = c(0,300)) +
#scale_y_continuous(limits = c(0,300))
#plot(my_data$Net.Profit.Loss~my_data$Total.expenses)
#abline(mb_lm, col="blue", lwd=3)
#+ geom_smooth(method = lm) 
```

                 colour = 'red'---rural  | colour = 'dark blue'---urban

slope = -0.69866, intercept = 6632.99072 \| slope = -0.69866, intercept = 6824.647 \| All slope = -0.86964, intercept = 7933.03356 \| slope = -0.86964, intercept = 8210.962 \| 2dig slope = -0.67259, intercept = 6423.53835 \| slope = -0.67259, intercept = 6603.554 \| 3dig

##### Gross Margin

```{r}
my_data <- mb_lmdata
mb_lm_gross <- lm(Gross.margin....~Cost.of.sales..direct.expenses.....+Operating.expenses..indirect.expenses.....+Location.indicator...code, data=my_data) 
summary(mb_lm_gross)
```

```{r}
my_data <- mb_2digindlmdata
mb_lm_gross <- lm(Gross.margin....~Cost.of.sales..direct.expenses.....+Operating.expenses..indirect.expenses.....+Location.indicator...code, data=my_data) 
summary(mb_lm_gross)
```

```{r}
my_data <- mb_3digindlmdata
mb_lm_gross <- lm(Gross.margin....~Cost.of.sales..direct.expenses.....+Operating.expenses..indirect.expenses.....+Location.indicator...code, data=my_data) 
summary(mb_lm_gross)
```

#### Gross margin intersection

```{r}
my_data <- mb_lmdata
mb_lm_gross2 <- lm(Gross.margin....~Cost.of.sales..direct.expenses.....*Location.indicator...code+Operating.expenses..indirect.expenses.....*Location.indicator...code, data=my_data) 
summary(mb_lm_gross2)
```

```{r}
my_data <- mb_2digindlmdata
mb_lm_gross2 <- lm(Gross.margin....~Cost.of.sales..direct.expenses.....*Location.indicator...code+Operating.expenses..indirect.expenses.....*Location.indicator...code, data=my_data) 
summary(mb_lm_gross2)
```

```{r}
my_data <- mb_3digindlmdata
mb_lm_gross2 <- lm(Gross.margin....~Cost.of.sales..direct.expenses.....*Location.indicator...code+Operating.expenses..indirect.expenses.....*Location.indicator...code, data=my_data) 
summary(mb_lm_gross2)
```

###### PCA

## mb

```{r}
mb_pca <- read.csv("new_mb_pca.csv", as.is = TRUE)
```


```{r}

names(mb_pca)
```


```{r}
my_data <- mb_pca[,-c(1:6)]
```

```{r}
my_data
```



```{r}
prcomp(my_data, scale.=TRUE)
```

```{r}
mbpca <- prcomp(my_data, scale.=TRUE)
summary(mbpca)
```

```{r}
plot(mbpca, type="lines", npcs=26)
```

```{r}
loadi <- round(mbpca$rotation[,1:5], 2)
loadi[abs(loadi)<0.2] <- NA
loadi
```

```{r}
biplot(mbpca)
```

```{r}
head(mb[order(mbpca$x[,1], decreasing=TRUE),c(3,5,6)])
```

```{r}
tail(mb[order(mbpca$x[,1], decreasing=TRUE),c(3,5,6)])
```

```{r}
head(mb[order(mbpca$x[,2], decreasing=TRUE),c(3,5,6)])
```

```{r}
tail(mb[order(mbpca$x[,2], decreasing=TRUE),c(3,5,6)])
```

```{r}
head(mb[order(mbpca$x[,3], decreasing=TRUE),c(3,5,6)])
```

```{r}
tail(mb[order(mbpca$x[,3], decreasing=TRUE),c(3,5,6)])

```

## mb_2dig

```{r}
my_data <- mb_2digindlmdata[,-c(1, 8, 9)]
mbpca_2dig <- prcomp(my_data, scale.=TRUE)
summary(mbpca_2dig)
```

```{r}
plot(mbpca_2dig, type="lines", npcs=26)
```

```{r}
loadi_2dig <- round(mbpca_2dig$rotation[,1:5], 2)
loadi_2dig[abs(loadi_2dig)<0.2] <- NA
loadi_2dig
```

```{r}
biplot(mbpca_2dig)
```

```{r}
head(mb_2digind[order(mbpca_2dig$x[,1], decreasing=TRUE),c(3,5,6)])
```

```{r}
tail(mb_2digind[order(mbpca_2dig$x[,1], decreasing=TRUE),c(3,5,6)])
```

```{r}
head(mb_2digind[order(mbpca_2dig$x[,2], decreasing=TRUE),c(3,5,6)])
```

```{r}
tail(mb_2digind[order(mbpca_2dig$x[,2], decreasing=TRUE),c(3,5,6)])
```

```{r}
head(mb_2digind[order(mbpca_2dig$x[,3], decreasing=TRUE),c(3,5,6)])
```

```{r}
tail(mb_2digind[order(mbpca_2dig$x[,3], decreasing=TRUE),c(3,5,6)])

```

## mb_3dig

```{r}
my_data <- mb_3digindlmdata[,-c(1, 8, 9)]
mbpca_3dig <- prcomp(my_data, scale.=TRUE)
summary(mbpca_3dig)
```

```{r}
plot(mbpca_3dig, type="lines", npcs=26)
```

```{r}
loadi_3dig <- round(mbpca_3dig$rotation[,1:5], 2)
loadi_3dig[abs(loadi_3dig)<0.2] <- NA
loadi_3dig
```

```{r}
biplot(mbpca_3dig)
```

```{r}
head(mb_3digind[order(mbpca_3dig$x[,1], decreasing=TRUE),c(3,5,6)])
```

```{r}
tail(mb_3digind[order(mbpca_3dig$x[,1], decreasing=TRUE),c(3,5,6)])
```

```{r}
head(mb_3digind[order(mbpca_3dig$x[,2], decreasing=TRUE),c(3,5,6)])
```

```{r}
tail(mb_3digind[order(mbpca_3dig$x[,2], decreasing=TRUE),c(3,5,6)])
```

```{r}
head(mb_3digind[order(mbpca_3dig$x[,3], decreasing=TRUE),c(3,5,6)])
```

```{r}
tail(mb_3digind[order(mbpca_3dig$x[,3], decreasing=TRUE),c(3,5,6)])

```
